### 2013-02-14 doc/icml2013/algo.tex
add bib

%%% second moment
Regressing on $x$ provides only first-order
information.  The key insight is that to get more information about the
parameters, we need to consider regressing on higher order powers,
analogous to consider higher order moments in method of moments estimators.
Let us then consider regressing $y^2$ on $x^\otimes$:
\begin{align}
  y^2 &= \innerp{\beta_h\tp{2}}{x\tp{2}} + \epsilon \innerp{\beta_h\tp{2}}{x\tp{2}} + \epsilon^2 \label{eq:y2}.
\end{align}

>>>>

%%% second moment
Regressing on $x$ provides only first-order
information.  The key insight is that
since higher-order moments usually yield more information,
let us consider regressing $y^2$ on $x^{\otimes 2}$:
\begin{align}
  y^2 &= \innerp{M_2}{x\tp{2}} + \epsilon \innerp{\beta_h\tp{2} - M_2}{x\tp{2}} + \epsilon^2 \label{eq:y2}.
\end{align}
